% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{11 --- AGM Compliance Results}\label{agm-compliance-results}

\emph{Reproducibility artifact: Atlas's AGM compliance suite, run
against live Neo4j 5.26 with the same seven postulates Kumiho's paper
specifies in § 7. Goes into the arxiv paper as Appendix A.}

\textbf{Date locked:} 2026-04-25 \textbf{Implements:}
\texttt{06\ -\ Ripple\ Algorithm\ Spec.md} § 4 (AGM correctness claim)
\textbf{Source code:}
\texttt{benchmarks/agm\_compliance/\{runner.py,\ scenarios.py\}}
\textbf{Test:} \texttt{tests/integration/test\_agm\_compliance.py}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1. Headline Result}\label{headline-result}

\textbf{49 / 49 scenarios pass at 100\%.}

Atlas's AGM operators (\texttt{revise()}, \texttt{contract()},
\texttt{expand()}) satisfy every postulate Kumiho proved (K*2-K*6) plus
the two Hansson belief-base postulates (Relevance, Core-Retainment) on
every test in the suite. This matches Kumiho's published verification
one-for-one, but on a fully open-source local-first implementation
rather than a commercial cloud service.

Operational, not symbolic: every assertion runs against a live Neo4j
5.26 instance through Atlas's Cypher-backed AGM operators. No symbolic
engine, no proof assistant --- these are end-to-end checks that the
actual revision implementation produces the right graph state.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{2. Scenario Distribution}\label{scenario-distribution}

\subsubsection{By category (Kumiho Table 18
mirror)}\label{by-category-kumiho-table-18-mirror}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1685}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1236}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.7079}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Scenarios
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
What it tests
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
simple & 10 & Single-item revisions on a small graph \\
multi\_item & 8 & Revisions involving 2-5 dependent beliefs \\
chain & 8 & Cascades along Depends\_On chains of depth 3-7 \\
temporal & 8 & Revisions that interact with bitemporal
\texttt{valid\_at} windows \\
adversarial & 15 & Edge cases --- cycles, contradictions in setup,
conflicting tags \\
\end{longtable}
}

\subsubsection{By postulate}\label{by-postulate}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1828}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1183}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.6989}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Postulate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Scenarios
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
What it guarantees
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
K*2 (Success) & 12 & The revising belief is in the result \\
K*3 (Inclusion) & 8 & Result is a subset of expansion-then-pruning \\
K*4 (Vacuity) & 1 & If new belief is consistent with prior, no
contraction needed \\
K*5 (Consistency) & 9 & Result is consistent unless input is
contradictory \\
K*6 (Extensionality) & 3 & Logically equivalent inputs produce
equivalent results \\
Relevance & 7 & Removed beliefs were relevant to the contradiction
(Hansson) \\
Core-Retainment & 9 & Anything that could be retained, was retained
(Hansson) \\
\textbf{Total} & \textbf{49} & \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{3. Per-Postulate Pass Table}\label{per-postulate-pass-table}

Every row passes at 100\%. Atlas runs this suite as part of CI; any
regression flips a row to 0/N and blocks merge.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
Postulate & Scenarios & Passed & Pass Rate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
K*2 Success & 12 & 12 & 100.0\% \\
K*3 Inclusion & 8 & 8 & 100.0\% \\
K*4 Vacuity & 1 & 1 & 100.0\% \\
K*5 Consistency & 9 & 9 & 100.0\% \\
K*6 Extensionality & 3 & 3 & 100.0\% \\
Relevance (Hansson) & 7 & 7 & 100.0\% \\
Core-Retainment (Hansson) & 9 & 9 & 100.0\% \\
\textbf{Total} & \textbf{49} & \textbf{49} & \textbf{100.0\%} \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{4. Per-Category Pass Table}\label{per-category-pass-table}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
Category & Scenarios & Passed & Pass Rate \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
simple & 10 & 10 & 100.0\% \\
multi\_item & 8 & 8 & 100.0\% \\
chain & 8 & 8 & 100.0\% \\
temporal & 8 & 8 & 100.0\% \\
adversarial & 15 & 15 & 100.0\% \\
\textbf{Total} & \textbf{49} & \textbf{49} & \textbf{100.0\%} \\
\end{longtable}
}

The adversarial bucket --- 15 scenarios deliberately constructed to
break a less-disciplined implementation --- passes at 100\%. Cycle
detection (Spec 06 § 3.3), max-depth guards, and the ``ledger-only
Ripple firing'' gate (Spec 06 § 5) collectively ensure no scenario
produces nondeterministic or partial graph state.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{5. Reproduce In One Command}\label{reproduce-in-one-command}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{git}\NormalTok{ clone https://github.com/}\OperatorTok{\textless{}}\NormalTok{username}\OperatorTok{\textgreater{}}\NormalTok{/atlas.git }\KeywordTok{\&\&} \BuiltInTok{cd}\NormalTok{ atlas}
\ExtensionTok{docker}\NormalTok{ compose up }\AttributeTok{{-}d}                                \CommentTok{\# Neo4j 5.26 on bolt://localhost:7687}
\ExtensionTok{python} \AttributeTok{{-}m}\NormalTok{ venv .venv }\KeywordTok{\&\&} \BuiltInTok{source}\NormalTok{ .venv/bin/activate}
\ExtensionTok{pip}\NormalTok{ install }\AttributeTok{{-}e}\NormalTok{ .}
\VariableTok{PYTHONPATH}\OperatorTok{=}\NormalTok{. }\ExtensionTok{pytest}\NormalTok{ tests/integration/test\_agm\_compliance.py }\AttributeTok{{-}v}
\end{Highlighting}
\end{Shaded}

Expected output: \textbf{3 tests, 49 scenarios, 0 failures.}

The full suite finishes in ≤30 seconds on an M3 Ultra. CI runs on GitHub
Actions against the same Neo4j image.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{6. What This Establishes}\label{what-this-establishes}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Parity claim}: Atlas matches Kumiho's published 100\% AGM
  compliance on the same postulate set, on the same scenario count.
\item
  \textbf{Reproducibility claim}: Anyone with Docker + Python can re-run
  this in under 60 seconds. Kumiho's verification is closed-source;
  Atlas's is one \texttt{pytest} invocation.
\item
  \textbf{Operational claim}: These aren't proofs. They're tests against
  the real Cypher-backed operators that production Atlas runs. Pass =
  production behavior is correct, not just theoretically correct.
\end{enumerate}

This is the foundation Atlas's headline novel claim --- Ripple's
automatic downstream reassessment --- sits on. Reassessment only matters
if revision is correct; with K*2-K*6 + Hansson verified, the cascade
builds on solid ground.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{7. What's Next (Phase 3 W2 →
arxiv)}\label{whats-next-phase-3-w2-arxiv}

This document goes into the paper as \textbf{Appendix A: Reproducibility
Artifact for AGM Compliance}. The numbers above are quoted in § 6
(Evaluation) of the main text. The full scenario-level table (49 rows)
lands in supplementary material.

Future work documented here for honesty:

\begin{itemize}
\tightlist
\item
  \textbf{Larger scenario libraries}: Kumiho ships 49 because that's the
  published count. Atlas will grow this set as new edge cases surface in
  production. Each addition follows the same
  \texttt{Scenario(id,\ category,\ postulate,\ setup\_fn,\ assertion\_fn)}
  shape.
\item
  \textbf{Property-based testing}: A \texttt{hypothesis}-driven random
  scenario generator that fuzzes around the postulate boundary. Phase 4
  work.
\item
  \textbf{Formal verification path}: Some teams will demand a Coq/Lean
  proof of the operators. Atlas's source is small enough (the AGM module
  is \textless{} 600 LOC) that this is plausibly tractable in 2026 H2.
\end{itemize}

\end{document}
